A meta-analysis of mental rotation ability in the first years of life

### 2022-04-23 code/analysis.Rmd
Add output of heterogeneity
Update meta-regression

# Compute standard error of Cohen's d based on assumed correlation
# See Hedges' formula on p. 253 in http://dx.doi.org/10.20982/tqmp.14.4.p242
# This will need a sensitivity analysis regarding the values of `r_assumed`
r_assumed <- 0.5
dat_all %>%
  mutate(
    ni = sample_size,
    vi = (dfi / (dfi - 2)) * ((2 * (1 - r_assumed)) / ni) *
      (1 + gi^2 * (ni / (2 * (1 - r_assumed)))) - (gi^2 / ji^2),
    sei = sqrt(vi)
  ) %>%
  filter(!is.na(gi)) %>%
  select(
    article,
    group,
    experiment,
    gender_split,
    gi,
    ni,
    vi,
    sei,
    female_percent,
    age_mean
  ) -> dat_all_r

@@

# We go ahead with the last solution as to use the maximum amount of information
# while not biasing the gender results
dat_select <- dat_both_mixed

# Recode predictor variables for meta-regression and plotting
dat_select %>%
  mutate(

  # Gender as a categorical variable
  gender = case_when(
    female_percent == 1.0 ~ "female",
    female_percent == 0.0 ~ "male",
    TRUE ~ "mixed"
  ) %>% factor(levels = c("mixed", "female", "male")),

  # Mean sample age in months, centered around the mean
  age = age_mean / 30.417,
  age = age - mean(age, na.rm = TRUE),
  .keep = "unused"

) -> dat
```

@@

@@

```{r, meta_regression}
# Apply sliding difference contrast coding for the gender categories
# This means that the Intercept will be the grand mean (i.e., the average across
# studies) whereas the betas will test female vs. mixed and male vs. female
(contrasts(dat$gender) <- MASS::contr.sdif(3))

# Meta-regression with gender
res_gender <- rma.mv(
  gi, vi,
  mods = ~ gender - 1,
  random = ~ 1 | article / experiment,
  data = dat,
  slab = experiment
)
print(res_gender)
# forest(res_gender)

# Pairwise comparison between the gender groups
anova(res_gender, X = rbind(c(-1, 1, 0), c(-1, 0, 1), c(0, -1, 1)))

# Meta-regression with age
res_age <- rma.mv(
  gi, vi,
  mods = ~age,
  random = ~ 1 | article / experiment,
  data = dat,
  slab = experiment
)
print(res_age)
# forest(res_age)

# Meta-regression with gender, age, and their interaction
res_full <- rma.mv(
  gi, vi,
  mods = ~ gender * age,
  random = ~ 1 | article / experiment,
  data = dat,
  slab = experiment
)
print(res_full)
# forest(res_full)
```

>>>>

# Compute standard error of Cohen's d based on assumed correlation
# See Hedges' formula on p. 253 in http://dx.doi.org/10.20982/tqmp.14.4.p242
# This will need a sensitivity analysis regarding the values of `r_assumed`
r_assumed <- 0.5
dat_all %>%
  mutate(
    ni = sample_size,
    vi = (dfi / (dfi - 2)) * ((2 * (1 - r_assumed)) / ni) *
      (1 + gi^2 * (ni / (2 * (1 - r_assumed)))) - (gi^2 / ji^2),
    sei = sqrt(vi)
  ) %>%
  filter(!is.na(gi)) %>%
  select(
    article,
    group,
    experiment,
    gender_split,
    gi,
    ni,
    vi,
    sei,
    female_percent,
    age_mean,
    age_sd,
    age_min,
    age_max,
    task
  ) -> dat_all_r

@@

# We go ahead with the last solution as to use the maximum amount of information
# while not biasing the gender results
dat <- dat_both_mixed
```

@@

# Check heterogeneity
(i2 <- dmetar::var.comp(res_ml))
# plot(i2)

# Check share of variance at each level of the model
round(res_ml$sigma2[1] / sum(res_ml$sigma2), 3) # Between-article (ICC)
round(res_ml$sigma2[2] / sum(res_ml$sigma2), 3) # Within-article (between-exp.)

@@

```{r, meta_regression}
# Recode predictor variables for meta-regression and plotting
dat %>%
  mutate(

    # Gender as a categorical (factor) variable
    gender_f = case_when(
      female_percent == 1.0 ~ "Female",
      female_percent == 0.0 ~ "Male",
      TRUE ~ "Mixed"
    ) %>% factor(levels = c("Mixed", "Female", "Male")),
    # Re-code as contrast for the meta-regression model
    gender = recode(gender_f, "Mixed" = 0, "Female" = -0.5, "Male" = 0.5),

    # Mean sample age in years, centered around the mean
    age = age_mean / 365.25,
    age_c = age - mean(age, na.rm = TRUE),
    age_sd = age_sd / 365.25,

    # Task type as a categorical (factor) variale
    task_f = factor(task, levels = c("Habituation", "VoE")),
    # Re-code as contrast for the meta-regression model
    task = recode(task_f, "Habituation" = -0.5, "VoE" = 0.5),
    .keep = "unused"
  ) -> dat_reg

# Meta-regression with gender, age, and task
res_reg <- rma.mv(
  gi, vi,
  mods = ~ gender * age_c + task,
  random = ~ 1 | article / experiment,
  data = dat_reg,
  slab = experiment
)
print(res_reg)
# forest(res_full)
```

```{r, meta_regression_bayes}
# Specify priors
prior_c <- c(
  set_prior("normal(0, 1)", class = "Intercept"),
  set_prior("normal(0, 0.5)", class = "b"),
  set_prior("cauchy(0, 0.3)", class = "sd")
)

# Run prior predictive simulation
res_prior_reg <- brm(
  gi | se(sei) ~ gender * age_c + task + (1 | article / experiment),
  data = dat_reg,
  prior = prior_c,
  sample_prior = "only",
  save_pars = save_pars(all = TRUE),
  chains = 4,
  iter = 10000,
  cores = 4,
  control = list(adapt_delta = 0.99)
)
summary(res_prior_reg)
# plot(res_prior_reg)

# Run Bayesian multilevel model
res_brm_reg <- update(res_prior_reg, sample_prior = FALSE)
summary(res_brm_reg)
# plot(res_brm_reg)
```

```{r, fig_regression}
# Plot regression with gender and age
alph <- 0.7
dat_reg %>%
  ggplot(aes(x = age * 12, y = gi, color = gender_f)) +
  # Data points
  # geom_errorbar(aes(xmin = age - age_sd, xmax = age + age_sd), alpha = alph) +
  # geom_errorbar(aes(ymin = gi - sei, ymax = gi + sei), alpha = alph) +
  geom_point(aes(size = ni), shape = 16, alpha = alph) +
  # Regression lines - currently not reflecting the meta-analytic model
  geom_smooth(method = lm, formula = y ~ x, alpha = .1) +
  # Styling
  scale_x_continuous(limits = c(3, 16), breaks = seq(4, 16, 2)) +
  scale_y_continuous(limits = c(-1.3, 2.5), breaks = seq(-1, 2.5, 0.5)) +
  scale_color_brewer(palette = "Dark2") +
  labs(
    x = "Age (months)",
    y = expression("Hedges'" ~ italic("g")),
    color = "Gender",
    size = "Sample size"
  ) +
  theme_bw() +
  theme(
    panel.border = element_rect(size = 1),
    panel.grid = element_line(color = "grey90"),
    text = element_text(family = "Helvetica"),
  )

# Save the plot
ggsave(here(figures_dir, "regression.pdf"), width = 7, height = 4)
```
